SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-04 response.tex

% 感谢您指出第9页左侧第三段中提到的几个“步骤”未在文本中得到充分解释的问题。我们认识到这些步骤没有得到适当的说明，这可能会导致读者的困惑。但是其实，这4个step对应着ong-term Attack Intention Detection的4个步骤。

% 为了解决这个问题，我们已经修订了该段落，以提供对每个提到的步骤的详细解释。具体来说，我们现在：

% 定义每个步骤：我们澄清了每个步骤的内容，包括其目的以及它如何融入到手稿中讨论的整体过程。

% 提供上下文：我们增加了与前文讨论相关的上下文信息，帮助读者理解这些步骤在更广泛框架中的重要性。

% 举例说明：在适用的情况下，我们添加了示例，以说明每个步骤的执行方式，使读者更容易理解所呈现概念的实际应用。

% 这些修改增强了段落的清晰度和可理解性，确保读者能够跟随预期的逻辑，并理解每个步骤在该过程中的重要性。我们非常感谢您的反馈，这对改进手稿的这一部分起到了重要作用。

Thank you for your observation regarding the mention of several "steps" in the third paragraph of the left column on page 9. We acknowledge that these steps were not adequately explained, which may lead to confusion for the reader. But in fact, these four steps correspond to the four steps of ong term attack intention detection.

To address this issue, we have revised the paragraph to provide a detailed explanation of each step mentioned. Specifically, we now:

Define Each Step: We clarify what each step entails, including its purpose and how it fits into the overall process discussed in the manuscript.

Provide Context: We include contextual information that connects the steps to the preceding discussion, helping readers understand their significance within the broader framework.

Illustrate with Examples: Where applicable, we have added examples to illustrate how each step is executed, making it easier for readers to grasp the practical application of the concepts presented.

These modifications enhance the clarity and comprehensibility of the paragraph, ensuring that readers can follow the intended logic and understand the importance of each step in the process. We appreciate your feedback, which has been instrumental in improving this section of the manuscript.

\textcolor{blue}{We summarize the algorithm in the form of pseudocode, as shown in Algorithm 2. Lines 4 to 6 correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds. Lines 7 to 12 correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level. Lines 13 to 22 correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm. Finally, lines 23 to 25 correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.}

% comment20
\rcomment{
\color{red} The manuscript’s language requires improvement, as there are multiple grammatical errors and unclear expressions. A thorough revision is suggested to enhance overall readability.
}
\textbf{Response:} 
Thank you for your valuable feedback. We appreciate your comments regarding the grammatical errors and unclear expressions in the manuscript.
In response, we have undertaken a comprehensive revision of the paper, with particular attention to correcting grammatical mistakes and improving the clarity of the text. We have also simplified complex expressions and enhanced the overall readability to ensure the content is more accessible and coherent.

@@

\textcolor{blue}{
Due to the curse of dimensionality in high-dimensional spaces, traditional methods based on shallow semantic
feature can no longer effectively identify malicious nodes. In contrast, once model updates are transformed into the frequency domain, their differences are primarily concentrated in the low-frequency components. Focusing on the analysis of these low-frequency components not only improves identification accuracy but also significantly reduces computational overhead. For each update \(\triangledown \theta_i^t\), we apply one-dimensional DCT-II[35] to obtain its corresponding frequency distribution. Then we extract $m$ low-frequency components[36], such as 5000, yielding the low-frequency vector $G_i^t$.
}

%========================================================
\rcomment{
\color{red} In Algorithm 1, there are unused variables in line 5.
}
% 问题：算法1第5行出现未使用变量。

\textbf{Response:} We thank the Reviewer for the constructive comment, and
% 非常抱歉，因为我们的疏忽，导致该算法出现让人无法理解的地方。根据您的建议，我们修改了该算法的相关部分，删除了未使用的变量。同时为了使整个算法过程更易理解，我们修改了另外一些跟原文不一致的地方，\ref{alg:malicious-node-detection}展示了修改后的结果。
we sincerely apologize for the confusion caused by the oversight in our algorithm.
Following your suggestion, we revised the relevant parts of the algorithm and removed unused variables.
Additionally, to make the entire algorithm process easier to understand, we adjusted some parts that were inconsistent with the original text, and algorithm \ref{alg:malicious-node-detection} shows the modified result.
% 最后，为了表现算法中某些变量会随训练轮次所变化，我们给一些变量添加时间$t$的上标，比如修改$C_{max},Chi_i^2,{C_1}', {C_2}'$至$C^t_{max},{Chi^t_i}^2,{C^t_1}', {C^t_2}'$
Finally, to represent that certain variables in the algorithm change with the training rounds, we added the superscript of round $t$ to some variables, such as modifying $C_{max}, Chi_i^2, {C'_1}, {C'_2}$ to $C^t_{max}, {Chi^t_i}^2, {C^t_1}', {C^t_2}'$.

% 图1展示了算法修改后的结果
The \ref{alg:malicious-node-detection} shows the version after modification.

@@

\multirow{4}{*}{\textcolor{blue}{Angle}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.88} & \textcolor{blue}{0.73} & \textcolor{blue}{0.06} & \textcolor{blue}{0.27} & \textcolor{blue}{0.84} & \textcolor{blue}{0.68} \\ 
                       & \textcolor{blue}{FLTrust}   & \textcolor{blue}{0.86} & \textcolor{blue}{0.60} & \textcolor{blue}{0.03} & \textcolor{blue}{0.40} & \textcolor{blue}{0.80} & \textcolor{blue}{0.65} \\ 
                       & \textcolor{blue}{Flame}     & \textcolor{blue}{0.90} & \textcolor{blue}{0.67} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.33} & \textcolor{blue}{0.83} & \textcolor{blue}{0.76} \\ 
                       & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{0.96}} & \textbf{\textcolor{blue}{0.87}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.13}} & \textbf{\textcolor{blue}{0.94}} & \textbf{\textcolor{blue}{0.88}} \\ \hline
\end{tabular}
}
\vspace{1em}
\begin{tablenotes}
\scriptsize
\item ``Acc." stands for Accuracy, ``Rec." for Recall, ``FPR" for False Positive Rate, ``FNR" for False Negative Rate, ``AUC" for Area Under Curve, and ``MCC" for Matthews Correlation Coefficient. The strategies are abbreviated as ``None" (No strategy), ``Size" (Size-limited strategy), and ``Angle" (Angle-limited strategy).
\end{tablenotes}
\label{tab:detect}
\end{table}

\newpage

\section{Responses to the Comments from Reviewer 4}

% comment12
\rcomment{
\color{red} Why does the section on "Instantaneous Attack Behavior Perception" use the chi-square distribution to calculate outlier differences instead of cosine similarity? The manuscript lacks an explanation for this choice.
}
\textbf{Response:} 
We appreciate the reviewer’s insightful feedback. The decision to use the chi-square distribution instead of cosine similarity is rooted in the nature of the feature distribution in the frequency domain. Cosine similarity, while useful for comparing the angle between two vectors, would not appropriately capture the frequency domain’s distributional features in our model, where the outlier differences are more pronounced in the low-frequency components rather than in directional changes. The chi-square distribution allows us to better distinguish between malicious updates, which tend to introduce subtle but consistent deviations in these low-frequency features, and benign updates. This approach enhances attack behavior perception accuracy by weighting the significant deviations while minimizing the impact of noise in the higher-frequency components.
